---
title: "cropReprojectLCC2005"
author: "Tati Micheletti, Eliot McIntire and Alex Chubaty"
date: "05 May 2018"
output: pdf_document
---

STILL NEED TO FIX: [FIX]
- rasterToMatch not working: not completing nor returning error / warning (failing silently)

## Overview

This is a translator module that crops and reprojects the data from the [Landcover Classification 2005 data set](ftp://ftp.ccrs.nrcan.gc.ca/ad/NLCCLandCover/LandcoverCanada2005_250m/LandCoverOfCanada2005_V1_4.zip) and the 1000m age map data set from Pan et al. 2012. They are both returned in the projection of the LCC2005 data set.

## Module Info

This is entirely drawn from an unpublished document from the BEACONS team. 

## Literature Cited

Pan, Y., J. M. Chen, R. Birdsey, K. McCullough, L. He, and F. Deng. 2012. NACP Forest Age Maps at 1-km Resolution for Canada (2004) and the U.S.A. (2006). Data set. Available on-line [http://daac.ornl.gov] from ORNL DAAC, Oak Ridge, Tennessee, U.S.A. http://dx.doi.org/10.3334/ORNLDAAC/1096

## Usage

This module doesn't require parameters or objects, but it is possible to select specific study areas to crop the analysis to.

### Loading libraries and setting up the paths  

```{r module_usage}
library(SpaDES)

# Set the directories
  workDirectory <- getwd()
  
  paths <- list(
    cachePath = file.path(workDirectory, "cache"),
    modulePath = file.path(workDirectory, "modules"),
    inputPath = file.path(workDirectory, "inputs"),
    outputPath = file.path(workDirectory, "outputs")
  )
  
  setPaths(modulePath = paths$modulePath, inputPath = paths$inputPath, outputPath = paths$outputPath, cachePath = paths$cachePath)
```

### Defining the Parameters and Objects

The user defined parameters for this module are:
*.useCache*: Should this entire module be run with caching activated? This is generally intended for data-type modules, where stochasticity and time are not relevant. Default is `FALSE`.
*plotCroppedRasters*: Should the vegMap and ageMap be plotted? Default is `TRUE`.

The objects that one can specify for this module are:
*cropTemplate*: Choose among `rP` for randomPolygon or `eD` for ecodistrict.

If cropTemplate == 'rP'
*polyMatrix*: This is the latlong center point for the random polygon. Default is a random forested area in British Columbia (`-122.85, 52.04`).
*areaSize*: This is the size in hactares of the random polygon. Default is `500000` hactares.

If cropTemplate == 'eD'
*areaNumber*: This is the number of the ecodistrict to crop the maps to. The default is `339` (Athabasca Plain, Boreal Shield - Saskatchewan). To see a map of the available ecodistricts:

```{r ecod_map}
source(file.path(paths$modulePath, "cropReprojectLCC2005/R/ecodistrictMap.R"))
library('magick')
ecodistrictMap()
```

If deciding for ecodistrict `339` instead of a random polygon in BC, add the following objects to the objects' list below: 
`cropTemplate = "eD"`

If deciding for an ecodistrict different than the default (`339`), add the following objects to the objects' list below: 
`cropTemplate = "eD", areaNumber = NUMBER_OF_CHOSEN_ECODISTRICT`

Setting the parameters:

``` {r setting_parameters}
times <- list(start = 0, end = 0)
parameters <- list()
modules <- list("cropReprojectLCC2005")
objects <- list()
inputs <- list()
outputs <- list()
```

## Downloading data for the module (if you still don't have the data)

``` {r download_data}
downloadData(module = "cropReprojectLCC2005", path = paths$modulePath)
```

## Running the simulation  

``` {r running_simulation}
mySim <- simInit(times = times, params = parameters, modules = modules,objects = objects) # Initialization with module's checking
mySimOut <- spades(mySim) # Simulation
```
